Introduction to Natural Language Processing

### 2007-07-12 slides/baypiggies.tex
more on getting involved; more on case studies
svn/trunk@4879

\begin{frame}
  \frametitle{Notes}
  \begin{itemize}
    \item Text classification
    \item Distributional similarity
    \item Parsing
  \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{Classifying in NLTK}
  \begin{itemize}
    \item Classifiers are applied to \emph{featuresets}:
\begin{alltt}\small
>>> animal = dict(fur=True, legs=4, 
                  size='large', spots=True)
>>> my_classifier.classify(animal)
'leopard'
\end{alltt}
    \item Features are found with a \emph{feature extractor}:
\begin{alltt}\small
>>> def document_features(document):
...     return dict([('contains-word(%s)'%w,True) 
...                  for w in document])
\end{alltt}
    \item Training:
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Word Similarity?}
  \begin{itemize}
  \item It's useful to know whether two words are similar
    \begin{itemize}
    \item ...
    \end{itemize}
  \item Different notions of \emph{similarity}:
    \item What words tend to co-occur?
    \item What words occur in similar contexts?
  \end{itemize}
\end{frame}

@@

>>>>

\begin{frame}
  \frametitle{Notes}
  \begin{itemize}
    \item Text classification
    \item Word similarity
    \item Parsing
  \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{Classifying in NLTK}
  \begin{itemize}
    \item Classifiers are applied to \emph{featuresets}:
\begin{alltt}\small
>>> animal = dict(fur=True, legs=4, 
                  size='large', spots=True)
>>> my_classifier.classify(animal)
'leopard'
\end{alltt}
    \item Features are found with a \emph{feature extractor}:
\begin{alltt}\small
>>> def document_features(document):
...     return dict([('contains-word(%s)'%w,True) 
...                  for w in document])
\end{alltt}
    \item Training:
\begin{alltt}\small
>>> labeled_featuresets = [(document_features(doc), label)
..       .                 for (doc, label) in labeled_docs]
>>> classifier = NaiveBayesClassifier.train(labeled_docs)
\end{alltt}

  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Word Similarity}
  \begin{itemize}
  \item It's useful to know whether two words are similar
    \begin{itemize}
    \item Search: don't just find the exact terms you specify.
    \item Question Answering: handle synonyms.
    \item Parsing: what words act similarly to one another?
    \end{itemize}
  \item Different notions of \emph{similarity}:
  \item What words tend to co-occur?
  \item What words occur in similar contexts?
  \end{itemize}
\end{frame}

\subsection{Parsing}

\begin{frame}
  \frametitle{Parsing}
  \begin{itemize}
  \item Chart Parsing Demo
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Getting Involved}
  \begin{itemize}
  \item http://nltk.org/
    \begin{itemize}
    \item http://nltk.org/index.php/Development
    \item http://nltk.org/index.php/Chatroom
    \end{itemize}
  \item Mailing lists:
    \begin{itemize}
    \item nltk-devel@lists.sourceforge.net
    \item nltk-announce@lists.sourceforge.net
    \item nltk-users@lists.sourceforge.net
    \end{itemize}
  \end{itemize}
\end{frame}
